---
title: "Doubly Robust Estimation for 1980 Results"
output: pdf_document
---

```{r}
library(rstudioapi)
library(haven)
library(dplyr)
library(ggplot2)
library(readr)
library(measurements)
library(geosphere)
library(tidyr)
library(kableExtra)
```

```{r}
# load data
raw_path <- paste0(dirname(getSourceEditorContext()$path), '/data/raw/')
processed_path <- paste0(dirname(getSourceEditorContext()$path), '/data/processed/')
census1980 <- readRDS(paste0(processed_path, 'census1980_clean.Rda'))
```

```{r}
# subset the data
reg_dat <- census1980 %>% select(hsspend_at_four, fs_available, female, momhsdrop,
                                 momhsgrad, blacknh, othernh, hispanic, 
                                 full_cty_fips, stname, schoolstart, 
                                 preschool1969, pred_cov, at_gradelvl, whitenh)
```

```{r}
# binarize the treatment to be yes if your coverage is greater than 50%
reg_dat <- reg_dat %>% mutate(treated = as.integer(reg_dat$pred_cov >= 50))
```

```{r}
models <- vector(mode = 'list', 12)
```

We will assume that the treatment labels are fixed for now (i.e. not the result
of estimation by us, but rather given to us with the sample).

Let's first fit the outcome regression models with this new definition of the treatment
variable.

```{r}
# pre-allocating the rows
row2 <- rep(0, 6)
row3 <- rep(0, 6)
row4 <- rep(0, 6)
row5 <- rep(0, 6)
row6 <- rep(0, 6)
```

# fitting only models with full sample, no fixed effects

```{r}
# fitting aggregate cohort logistic regresision models for each subgroup
models[[1]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool1969:treated, 
                     family = 'binomial', data = reg_dat)
models[[2]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool1969:treated, 
                     family = 'binomial', data = reg_dat %>% filter(female == 0))
models[[3]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool1969:treated, 
                     family = 'binomial', data = reg_dat %>% filter(female == 1))
models[[4]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + momhsdrop + female +
                       momhsgrad + preschool1969:treated, 
                     family = 'binomial', data = reg_dat %>% filter(whitenh == 1))
models[[5]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + preschool1969:treated, 
                     family = 'binomial', data = reg_dat %>% filter(blacknh == 1))
models[[6]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + preschool1969:treated, 
                     family = 'binomial', data = reg_dat %>% filter(hispanic == 1))
```

```{r}
# fitting disaggregated logistic models for each subgroup
reg_dat <- reg_dat %>% mutate(preschool6768 = as.integer(reg_dat$schoolstart >= 1967 & reg_dat$schoolstart <= 1968)) %>%
  mutate(preschool69 = as.integer(reg_dat$schoolstart == 1969)) %>%
  mutate(preschool7072 = as.integer(reg_dat$schoolstart >= 1970 & reg_dat$schoolstart <= 1972)) %>%
  mutate(preschool7374 = as.integer(reg_dat$schoolstart >= 1973 & reg_dat$schoolstart <= 1974))

models[[7]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool6768:treated + 
                       preschool69:treated + preschool7072:treated + preschool7374:treated, 
                     family = 'binomial', data = reg_dat)
models[[8]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool6768:treated + 
                       preschool69:treated + preschool7072:treated + preschool7374:treated, 
                     family = 'binomial', data = reg_dat %>% filter(female == 0))
models[[9]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool6768:treated + 
                       preschool69:treated + preschool7072:treated + preschool7374:treated, 
                     family = 'binomial', data = reg_dat %>% filter(female == 1))
models[[10]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + preschool6768:treated + 
                       preschool69:treated + preschool7072:treated + preschool7374:treated, 
                     family = 'binomial', data = reg_dat %>% filter(whitenh == 1))
models[[11]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + preschool6768:treated + 
                       preschool69:treated + preschool7072:treated + preschool7374:treated, 
                     family = 'binomial', data = reg_dat %>% filter(blacknh == 1))
models[[12]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + preschool6768:treated + 
                       preschool69:treated + preschool7072:treated + preschool7374:treated, 
                     family = 'binomial', data = reg_dat %>% filter(hispanic == 1))
```

```{r}
# function to estimate the average partial effect (outcome imputation estimator)
# takes in the fitted logistic model, creates outcome regression models for treatment
# and control, and computes outcome imputation estimates for subgroups of interest
averagePartialEffect1 <- function(subdat, model, returnMus=F) {
  
  dat <- model$data
  mu1mod <- glm(update(model$formula, ~ . - preschool1969:treated + preschool1969), family = 'binomial', data = dat %>% filter(treated == 1))
  mu0mod <- glm(update(model$formula, ~ . - preschool1969:treated), family = 'binomial', data = dat %>% filter(treated == 0))
  mu1s <- predict(mu1mod, subdat, type = 'response')
  mu0s <- predict(mu0mod, subdat, type = 'response')
  
  if (returnMus) {
    return(cbind(mu1s, mu0s))
  }
  return(mean(mu1s - mu0s))
  
}

# same as above, except this is used for the disaggregated cohort specification
averagePartialEffect2 <- function(subdat, model, returnMus=F) {
  
  dat <- model$data
  mu1form <- update(model$formula, ~ . - preschool6768:treated - preschool69:treated - 
           preschool7072:treated - preschool7374:treated + preschool6768 + preschool69 + preschool7072 + preschool7374)
  mu0form <- update(model$formula, ~ . - preschool6768:treated - preschool69:treated - 
           preschool7072:treated - preschool7374:treated)
  mu1mod <- glm(mu1form, family = 'binomial', data = dat %>% filter(treated == 1))
  mu0mod <- glm(mu0form, family = 'binomial', data = dat %>% filter(treated == 0))
  mu1s <- predict(mu1mod, subdat, type = 'response')
  mu0s <- predict(mu0mod, subdat, type = 'response')
  
    if (returnMus) {
    return(cbind(mu1s, mu0s))
  }
  return(mean(mu1s - mu0s))
  
}
```

```{r}
# pre-allocating the rows
row2 <- rep(0, 6)
row3 <- rep(0, 6)
row4 <- rep(0, 6)
row5 <- rep(0, 6)
row6 <- rep(0, 6)

# getting APE estimates for each group as before, using aggregated cohort specification
row2[1] <- averagePartialEffect1(reg_dat %>% filter(preschool1969==1), models[[1]])
row2[2] <- averagePartialEffect1(reg_dat %>% filter(preschool1969 == 1) %>% filter(female == 0), models[[2]])
row2[3] <- averagePartialEffect1(reg_dat %>% filter(preschool1969 == 1) %>% filter(female == 1), models[[3]])
row2[4] <- averagePartialEffect1(reg_dat %>% filter(preschool1969 == 1) %>% filter(whitenh == 1), models[[4]])
row2[5] <- averagePartialEffect1(reg_dat %>% filter(preschool1969 == 1) %>% filter(blacknh == 1), models[[5]])
row2[6] <- averagePartialEffect1(reg_dat %>% filter(preschool1969 == 1) %>% filter(blacknh == 1), models[[6]])
```

```{r}
# using disaggregated cohort specification, obtaining ATE estimates for each cohort subgroup
# within each demographic group
row3[1] <- averagePartialEffect2(reg_dat %>% filter(preschool6768==1), models[[7]])
row4[1] <- averagePartialEffect2(reg_dat %>% filter(preschool69==1), models[[7]])
row5[1] <- averagePartialEffect2(reg_dat %>% filter(preschool7072==1), models[[7]])
row6[1] <- averagePartialEffect2(reg_dat %>% filter(preschool7374==1), models[[7]])

row3[2] <- averagePartialEffect2(reg_dat %>% filter(preschool6768==1) %>% filter(female == 0), models[[8]])
row4[2] <- averagePartialEffect2(reg_dat %>% filter(preschool69==1) %>% filter(female == 0), models[[8]])
row5[2] <- averagePartialEffect2(reg_dat %>% filter(preschool7072==1) %>% filter(female == 0), models[[8]])
row6[2] <- averagePartialEffect2(reg_dat %>% filter(preschool7374==1) %>% filter(female == 0), models[[8]])

row3[3] <- averagePartialEffect2(reg_dat %>% filter(preschool6768==1) %>% filter(female == 1), models[[9]])
row4[3] <- averagePartialEffect2(reg_dat %>% filter(preschool69==1) %>% filter(female == 1), models[[9]])
row5[3] <- averagePartialEffect2(reg_dat %>% filter(preschool7072==1) %>% filter(female == 1), models[[9]])
row6[3] <- averagePartialEffect2(reg_dat %>% filter(preschool7374==1) %>% filter(female == 1), models[[9]])

row3[4] <- averagePartialEffect2(reg_dat %>% filter(preschool6768==1) %>% filter(whitenh == 1), models[[10]])
row4[4] <- averagePartialEffect2(reg_dat %>% filter(preschool69==1) %>% filter(whitenh == 1), models[[10]])
row5[4] <- averagePartialEffect2(reg_dat %>% filter(preschool7072==1) %>% filter(whitenh == 1), models[[10]])
row6[4] <- averagePartialEffect2(reg_dat %>% filter(preschool7374==1) %>% filter(whitenh == 1), models[[10]])

row3[5] <- averagePartialEffect2(reg_dat %>% filter(preschool6768==1) %>% filter(blacknh == 1), models[[11]])
row4[5] <- averagePartialEffect2(reg_dat %>% filter(preschool69==1) %>% filter(blacknh == 1), models[[11]])
row5[5] <- averagePartialEffect2(reg_dat %>% filter(preschool7072==1) %>% filter(blacknh == 1), models[[11]])
row6[5] <- averagePartialEffect2(reg_dat %>% filter(preschool7374==1) %>% filter(blacknh == 1), models[[11]])

row3[6] <- averagePartialEffect2(reg_dat %>% filter(preschool6768==1) %>% filter(hispanic == 1), models[[12]])
row4[6] <- averagePartialEffect2(reg_dat %>% filter(preschool69==1) %>% filter(hispanic == 1), models[[12]])
row5[6] <- averagePartialEffect2(reg_dat %>% filter(preschool7072==1) %>% filter(hispanic == 1), models[[12]])
row6[6] <- averagePartialEffect2(reg_dat %>% filter(preschool7374==1) %>% filter(hispanic == 1), models[[12]])

```

```{r}
tab4_df <- rbind(row2, row3, row4, row5, row6)
tab4_df <- round(data.frame(tab4_df), 4)
colnames(tab4_df) <- c('All', 'Boys', 'Girls', 'White, NH', 'Black, NH', 'Hispanic')
rownames(tab4_df) <- c('Preschool post-1969',
                       'Cohort 67-68',
                       'Cohort 69',
                       'Cohort 70-72',
                       'Cohort 73-74')

kable(tab4_df, caption = 'Estimates of ATE for different subpopulations.') %>% kable_classic()
```


```{r}
# function to make the doubly robust estimators for different datasets
# and models
getDRest <- function(subdat, model, prop_score, singleFixed) {
  
  if (singleFixed) {
    mus <- averagePartialEffect1(subdat, model, returnMus = T)
  }
  else {
    mus <- averagePartialEffect2(subdat, model, returnMus = T)
  }
  
  mu1s <- as.numeric(mus[,1])
  mu0s <- as.numeric(mus[,2])
  props <- predict(prop_score, subdat, type = 'response')
  trt <- subdat %>% select(treated) %>% pull()
  outcome <- subdat %>% select(at_gradelvl) %>% pull()

  mu1dr <- mean((trt*(outcome - mu1s))/props + mu1s) 
  mu0dr <- mean(((1-trt)*(outcome - mu0s))/(1-props) + mu0s)
  taudr <- mu1dr - mu0dr
  
  return(taudr)

}
```


```{r}
# let's first make the propensity score models for each subgroup (there are 12)
propmods <- vector(mode = 'list', 12)
propmods[[1]] <- glm(treated ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool1969, 
                  family = 'binomial', data = reg_dat)
propmods[[2]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic  + preschool1969, 
                  family = 'binomial', data = reg_dat %>% filter(female == 0))
propmods[[3]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool1969, 
                  family = 'binomial', data = reg_dat %>% filter(female == 1))
propmods[[4]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop + female +
                       momhsgrad + preschool1969, 
                  family = 'binomial', data = reg_dat %>% filter(whitenh == 1))
propmods[[5]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop + female +
                       momhsgrad + preschool1969, 
                  family = 'binomial', data = reg_dat %>% filter(blacknh == 1))
propmods[[6]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop + female +
                       momhsgrad + preschool1969, 
                  family = 'binomial', data = reg_dat %>% filter(hispanic == 1))
propmods[[7]] <- glm(treated ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool6768 + preschool69 + preschool7072 + preschool7374, 
                  family = 'binomial', data = reg_dat)
propmods[[8]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool6768 + preschool69 + preschool7072 + preschool7374, 
                  family = 'binomial', data = reg_dat %>% filter(female == 0))
propmods[[9]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool6768 + preschool69 + preschool7072 + preschool7374, 
                  family = 'binomial', data = reg_dat %>% filter(female == 1))
propmods[[10]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop + female +
                       momhsgrad + preschool6768 + preschool69 + preschool7072 + preschool7374, 
                  family = 'binomial', data = reg_dat %>% filter(whitenh == 1))
propmods[[11]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop + female +
                       momhsgrad + preschool6768 + preschool69 + preschool7072 + preschool7374, 
                  family = 'binomial', data = reg_dat %>% filter(blacknh == 1))
propmods[[12]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop + female +
                       momhsgrad + preschool6768 + preschool69 + preschool7072 + preschool7374, 
                  family = 'binomial', data = reg_dat %>% filter(hispanic == 1))
```

```{r}
# pre-allocating the rows
row2 <- rep(0, 6)
row3 <- rep(0, 6)
row4 <- rep(0, 6)
row5 <- rep(0, 6)
row6 <- rep(0, 6)

# getting DR estimates of ATE for each aggregated cohort subgroup within each demographic group
row2[1] <- getDRest(reg_dat %>% filter(preschool1969 == 1), models[[1]], propmods[[1]], T)
row2[2] <- getDRest(reg_dat %>% filter(preschool1969 == 1) %>% filter(female == 0), models[[2]], propmods[[2]], T)
row2[3] <- getDRest(reg_dat %>% filter(preschool1969 == 1) %>% filter(female == 1), models[[3]], propmods[[3]], T)
row2[4] <- getDRest(reg_dat %>% filter(preschool1969 == 1) %>% filter(whitenh == 1), models[[4]], propmods[[4]], T)
row2[5] <- getDRest(reg_dat %>% filter(preschool1969 == 1) %>% filter(blacknh == 1), models[[5]], propmods[[5]], T)
row2[6] <- getDRest(reg_dat %>% filter(preschool1969 == 1) %>% filter(blacknh == 1), models[[6]], propmods[[6]], T)
```

```{r}
# getting DR estimates of ATE for each disaggregated cohort subgroup within each demographic group
row3[1] <- getDRest(reg_dat %>% filter(preschool6768==1), models[[7]], propmods[[7]], F)
row4[1] <- getDRest(reg_dat %>% filter(preschool69==1), models[[7]], propmods[[7]], F)
row5[1] <- getDRest(reg_dat %>% filter(preschool7072==1), models[[7]], propmods[[7]], F)
row6[1] <- getDRest(reg_dat %>% filter(preschool7374==1), models[[7]], propmods[[7]], F)

row3[2] <- getDRest(reg_dat %>% filter(preschool6768==1) %>% filter(female == 0), models[[8]], propmods[[8]], F)
row4[2] <- getDRest(reg_dat %>% filter(preschool69==1) %>% filter(female == 0), models[[8]], propmods[[8]], F)
row5[2] <- getDRest(reg_dat %>% filter(preschool7072==1) %>% filter(female == 0), models[[8]], propmods[[8]], F)
row6[2] <- getDRest(reg_dat %>% filter(preschool7374==1) %>% filter(female == 0), models[[8]], propmods[[8]], F)

row3[3] <- getDRest(reg_dat %>% filter(preschool6768==1) %>% filter(female == 1), models[[9]], propmods[[9]], F)
row4[3] <- getDRest(reg_dat %>% filter(preschool69==1) %>% filter(female == 1), models[[9]], propmods[[9]], F)
row5[3] <- getDRest(reg_dat %>% filter(preschool7072==1) %>% filter(female == 1), models[[9]], propmods[[9]], F)
row6[3] <- getDRest(reg_dat %>% filter(preschool7374==1) %>% filter(female == 1), models[[9]], propmods[[9]], F)

row3[4] <- getDRest(reg_dat %>% filter(preschool6768==1) %>% filter(whitenh == 1), models[[10]],propmods[[10]], F)
row4[4] <- getDRest(reg_dat %>% filter(preschool69==1) %>% filter(whitenh == 1), models[[10]],propmods[[10]], F)
row5[4] <- getDRest(reg_dat %>% filter(preschool7072==1) %>% filter(whitenh == 1), models[[10]],propmods[[10]], F)
row6[4] <- getDRest(reg_dat %>% filter(preschool7374==1) %>% filter(whitenh == 1), models[[10]], propmods[[10]], F)

row3[5] <- getDRest(reg_dat %>% filter(preschool6768==1) %>% filter(blacknh == 1), models[[11]],propmods[[11]], F)
row4[5] <- getDRest(reg_dat %>% filter(preschool69==1) %>% filter(blacknh == 1), models[[11]],propmods[[11]], F)
row5[5] <- getDRest(reg_dat %>% filter(preschool7072==1) %>% filter(blacknh == 1), models[[11]], propmods[[11]], F)
row6[5] <- getDRest(reg_dat %>% filter(preschool7374==1) %>% filter(blacknh == 1), models[[11]], propmods[[11]], F)

row3[6] <- getDRest(reg_dat %>% filter(preschool6768==1) %>% filter(hispanic == 1), models[[12]],propmods[[12]], F)
row4[6] <- getDRest(reg_dat %>% filter(preschool69==1) %>% filter(hispanic == 1), models[[12]], propmods[[12]], F)
row5[6] <- getDRest(reg_dat %>% filter(preschool7072==1) %>% filter(hispanic == 1), models[[12]], propmods[[12]], F)
row6[6] <- getDRest(reg_dat %>% filter(preschool7374==1) %>% filter(hispanic == 1), models[[12]], propmods[[12]], F)
```

```{r}
tab4_df <- rbind(row2, row3, row4, row5, row6)
tab4_df <- round(data.frame(tab4_df), 4)
colnames(tab4_df) <- c('All', 'Boys', 'Girls', 'White, NH', 'Black, NH', 'Hispanic')
rownames(tab4_df) <- c('Preschool post-1969',
                       'Cohort 67-68',
                       'Cohort 69',
                       'Cohort 70-72',
                       'Cohort 73-74')

kable(tab4_df, caption = 'Doubly robust estimate of treatment effect for different subpopulations.') %>% kable_classic()
```
Results that we observed before is confirmed for the doubly robust estimator!
