---
title: "Doubly Robust Estimation for 1980 Results"
output: pdf_document
---

As is likely the case, our logistic regression model for the probability of being at
grade level is likely misspecified (missing confounders or incorrect model form).
This is especially apparent because the authors use a model unfamiliar to me (from
their STATA code, which I didn't really understand). So, one of us is wrong,
so it's useful to use a doubly robust estimator to get a second shot at asymptotic
consistency with the true average causal effect.

However, in the absence of time to do a full literature search on propensity score
methods for continuous treatment variables (as ours is), we will binarize the
treatment variable to indicate SS is available in your area if the coverage
is above average, otherwise it is unavailable. 
We will also use the model with the cohort-level fixed effects, since we want to 
include some fixed effects but have the model run relatively quickly in order to get
standard error estimates (other models would take too long to run using a bootstrap).
Also, if we were to use county level fixed effects for a propensity score model,
we would be able to uniquely determine the treatment levels the treatment itself
is at the county level.

```{r}
library(rstudioapi)
library(haven)
library(dplyr)
library(ggplot2)
library(readr)
library(measurements)
library(geosphere)
library(tidyr)
library(kableExtra)
```

```{r}
# load data
raw_path <- paste0(dirname(getSourceEditorContext()$path), '/data/raw/')
processed_path <- paste0(dirname(getSourceEditorContext()$path), '/data/processed/')
census1980 <- readRDS(paste0(processed_path, 'census1980_clean.Rda'))
```

```{r}
# subset the data
reg_dat <- census1980 %>% select(hsspend_at_four, fs_available, female, momhsdrop,
                                 momhsgrad, blacknh, othernh, hispanic, 
                                 full_cty_fips, stname, schoolstart, 
                                 preschool1969, pred_cov, at_gradelvl, whitenh)
```

```{r}
# binarize the treatment to be yes if your coverage is greater than 50%
reg_dat <- reg_dat %>% mutate(treated = as.integer(reg_dat$pred_cov >= 50))
```

```{r}
models <- vector(mode = 'list', 12)
```

We will assume that the treatment labels are fixed for now (i.e. not the result
of estimation by us, but rather given to us with the sample).

Let's first fit the outcome regression models with this new definition of the treatment
variable.

```{r}
# takes really long to fit all of the fixed effects (county level + state x birth cohort)
# starting with just not fitting the fixed effects
models[[1]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool1969:treated + factor(schoolstart), 
                     family = 'binomial', data = reg_dat)
row2[1] <- as.numeric(models[[1]]$coefficients['preschool1969:treated'])
```

```{r}
models[[2]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool1969:treated + factor(schoolstart), 
                     family = 'binomial', data = reg_dat %>% filter(female == 0))
row2[2] <- as.numeric(models[[2]]$coefficients['preschool1969:treated'])
```


```{r}
models[[3]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool1969:treated+ factor(schoolstart), 
                     family = 'binomial', data = reg_dat %>% filter(female == 1))
row2[3] <- as.numeric(models[[3]]$coefficients['preschool1969:treated'])
```

```{r}
models[[4]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + momhsdrop + female +
                       momhsgrad + preschool1969:treated+ factor(schoolstart), 
                     family = 'binomial', data = reg_dat %>% filter(whitenh == 1))
row2[4] <- as.numeric(models[[4]]$coefficients['preschool1969:treated'])
```

```{r}
models[[5]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + preschool1969:treated + factor(schoolstart), 
                     family = 'binomial', data = reg_dat %>% filter(blacknh == 1))

row2[5] <- as.numeric(models[[5]]$coefficients['preschool1969:treated'])
```

```{r}
models[[6]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + preschool1969:treated+ factor(schoolstart), 
                     family = 'binomial', data = reg_dat %>% filter(hispanic == 1))
row2[6] <- as.numeric(models[[6]]$coefficients['preschool1969:treated'])
```

I'm fitting the models a little bit different than they did; I think they include the demographic terms
even though they're subsetting by demographic variable which is kinda weird. 

## Model 2: As Close to Their Model 2, No Extra Fixed Effects

Next code is to replicate the next four rows of Table 4.

```{r}
reg_dat <- reg_dat %>% mutate(preschool6768 = as.integer(reg_dat$schoolstart >= 1967 & reg_dat$schoolstart <= 1968)) %>%
  mutate(preschool69 = as.integer(reg_dat$schoolstart == 1969)) %>%
  mutate(preschool7072 = as.integer(reg_dat$schoolstart >= 1970 & reg_dat$schoolstart <= 1972)) %>%
  mutate(preschool7374 = as.integer(reg_dat$schoolstart >= 1973 & reg_dat$schoolstart <= 1974))

models[[7]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool6768:treated + 
                       preschool69:treated + preschool7072:treated + preschool7374:treated + 
                       factor(schoolstart), 
                     family = 'binomial', data = reg_dat)

row3[1] <- as.numeric(models[[7]]$coefficients['preschool6768:treated'])
row4[1] <- as.numeric(models[[7]]$coefficients['treated:preschool69'])
row5[1] <- as.numeric(models[[7]]$coefficients['treated:preschool7072'])
row6[1] <- as.numeric(models[[7]]$coefficients['treated:preschool7374'])
```

```{r}
models[[8]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool6768:treated + 
                       preschool69:treated + preschool7072:treated + preschool7374:treated+ 
                       factor(schoolstart), 
                     family = 'binomial', data = reg_dat %>% filter(female == 0))

row3[2] <- as.numeric(models[[8]]$coefficients['preschool6768:treated'])
row4[2] <- as.numeric(models[[8]]$coefficients['treated:preschool69'])
row5[2] <- as.numeric(models[[8]]$coefficients['treated:preschool7072'])
row6[2] <- as.numeric(models[[8]]$coefficients['treated:preschool7374'])
```

```{r}
models[[9]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool6768:treated + 
                       preschool69:treated + preschool7072:treated + preschool7374:treated+ 
                       factor(schoolstart), 
                     family = 'binomial', data = reg_dat %>% filter(female == 1))

row3[3] <- as.numeric(models[[9]]$coefficients['preschool6768:treated'])
row4[3] <- as.numeric(models[[9]]$coefficients['treated:preschool69'])
row5[3] <- as.numeric(models[[9]]$coefficients['treated:preschool7072'])
row6[3] <- as.numeric(models[[9]]$coefficients['treated:preschool7374'])
```

```{r}
models[[10]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + preschool6768:treated + 
                       preschool69:treated + preschool7072:treated + preschool7374:treated+ 
                       factor(schoolstart), 
                     family = 'binomial', data = reg_dat %>% filter(whitenh == 1))

row3[4] <- as.numeric(models[[10]]$coefficients['preschool6768:treated'])
row4[4] <- as.numeric(models[[10]]$coefficients['treated:preschool69'])
row5[4] <- as.numeric(models[[10]]$coefficients['treated:preschool7072'])
row6[4] <- as.numeric(models[[10]]$coefficients['treated:preschool7374'])
```

```{r}
models[[11]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + preschool6768:treated + 
                       preschool69:treated + preschool7072:treated + preschool7374:treated+ 
                       factor(schoolstart), 
                     family = 'binomial', data = reg_dat %>% filter(blacknh == 1))

row3[5] <- as.numeric(models[[11]]$coefficients['preschool6768:treated'])
row4[5] <- as.numeric(models[[11]]$coefficients['treated:preschool69'])
row5[5] <- as.numeric(models[[11]]$coefficients['treated:preschool7072'])
row6[5] <- as.numeric(models[[11]]$coefficients['treated:preschool7374'])
```

```{r}
models[[12]] <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + preschool6768:treated + 
                       preschool69:treated + preschool7072:treated + preschool7374:treated+ 
                       factor(schoolstart), 
                     family = 'binomial', data = reg_dat %>% filter(hispanic == 1))

row3[6] <- as.numeric(models[[12]]$coefficients['preschool6768:treated'])
row4[6] <- as.numeric(models[[12]]$coefficients['treated:preschool69'])
row5[6] <- as.numeric(models[[12]]$coefficients['treated:preschool7072'])
row6[6] <- as.numeric(models[[12]]$coefficients['treated:preschool7374'])
```

```{r}
# making Table 4, but only giving the coefficients of the logit model

tab4_df <- rbind(row1, row2, row3, row4, row5, row6)
tab4_df <- round(data.frame(tab4_df), 4)
colnames(tab4_df) <- c('All', 'Boys', 'Girls', 'White, NH', 'Black, NH', 'Hispanic')
rownames(tab4_df) <- c('Proportion of at-grade level', 
                       'Preschool post-1969 x coverage rate',
                       'Coverage rate x 67-68',
                       'Coverage rate x 69',
                       'Coverage rate x 70-72',
                       'Coverage rate x 73-74')

kable(tab4_df, caption = 'Logistic regression coefficients of variable capturing causal effect of interest for different subgroups.') %>% kable_classic()
```

```{r}
tab4_df <- rbind(row2, row3, row4, row5, row6)
tab4_df <- round(exp(data.frame(tab4_df)), 2)
colnames(tab4_df) <- c('All', 'Boys', 'Girls', 'White, NH', 'Black, NH', 'Hispanic')
rownames(tab4_df) <- c('Preschool post-1969 x coverage rate',
                       'Coverage rate x 67-68',
                       'Coverage rate x 69',
                       'Coverage rate x 70-72',
                       'Coverage rate x 73-74')

kable(tab4_df, caption = 'Odds ratio of being at grade level when SS coverage is increased by 30 percentage points.') %>% kable_classic()
```
Let's also provide estimation of the average causal effect of sesame street coverage
for the relevant populations. This is also called the average partial effect or average
marginal effect, as given in the textbook. This is because the OR, while having
a causal interpretation, does not target the average causal effect.

```{r}
# function to estimate the average partial effect
averagePartialEffect <- function(dat, model) {
  
  mu1s_dat <- dat %>% mutate(treated = 1)
  mu0s_dat <- dat %>% mutate(treated = 0)
  mu1s <- predict(model, mu1s_dat, type = 'response')
  mu0s <- predict(model, mu0s_dat, type = 'response')
  
  return(mean(mu1s - mu0s))
  
}
```

```{r}
# pre-allocating the rows
row2 <- rep(0, 6)
row3 <- rep(0, 6)
row4 <- rep(0, 6)
row5 <- rep(0, 6)
row6 <- rep(0, 6)

# getting APE estimates for each group as before
row2[1] <- averagePartialEffect(reg_dat %>% filter(preschool1969==1), models[[1]])
row2[2] <- averagePartialEffect(reg_dat %>% filter(preschool1969 == 1) %>% filter(female == 0), models[[2]])
row2[3] <- averagePartialEffect(reg_dat %>% filter(preschool1969 == 1) %>% filter(female == 1), models[[3]])
row2[4] <- averagePartialEffect(reg_dat %>% filter(preschool1969 == 1) %>% filter(whitenh == 1), models[[4]])
row2[5] <- averagePartialEffect(reg_dat %>% filter(preschool1969 == 1) %>% filter(blacknh == 1), models[[5]])
row2[6] <- averagePartialEffect(reg_dat %>% filter(preschool1969 == 1) %>% filter(blacknh == 1), models[[6]])
```

```{r}
row3[1] <- averagePartialEffect(reg_dat %>% filter(preschool6768==1), models[[7]])
row4[1] <- averagePartialEffect(reg_dat %>% filter(preschool69==1), models[[7]])
row5[1] <- averagePartialEffect(reg_dat %>% filter(preschool7072==1), models[[7]])
row6[1] <- averagePartialEffect(reg_dat %>% filter(preschool7374==1), models[[7]])

row3[2] <- averagePartialEffect(reg_dat %>% filter(preschool6768==1) %>% filter(female == 0), models[[8]])
row4[2] <- averagePartialEffect(reg_dat %>% filter(preschool69==1) %>% filter(female == 0), models[[8]])
row5[2] <- averagePartialEffect(reg_dat %>% filter(preschool7072==1) %>% filter(female == 0), models[[8]])
row6[2] <- averagePartialEffect(reg_dat %>% filter(preschool7374==1) %>% filter(female == 0), models[[8]])

row3[3] <- averagePartialEffect(reg_dat %>% filter(preschool6768==1) %>% filter(female == 1), models[[9]])
row4[3] <- averagePartialEffect(reg_dat %>% filter(preschool69==1) %>% filter(female == 1), models[[9]])
row5[3] <- averagePartialEffect(reg_dat %>% filter(preschool7072==1) %>% filter(female == 1), models[[9]])
row6[3] <- averagePartialEffect(reg_dat %>% filter(preschool7374==1) %>% filter(female == 1), models[[9]])

row3[4] <- averagePartialEffect(reg_dat %>% filter(preschool6768==1) %>% filter(whitenh == 1), models[[10]])
row4[4] <- averagePartialEffect(reg_dat %>% filter(preschool69==1) %>% filter(whitenh == 1), models[[10]])
row5[4] <- averagePartialEffect(reg_dat %>% filter(preschool7072==1) %>% filter(whitenh == 1), models[[10]])
row6[4] <- averagePartialEffect(reg_dat %>% filter(preschool7374==1) %>% filter(whitenh == 1), models[[10]])

row3[5] <- averagePartialEffect(reg_dat %>% filter(preschool6768==1) %>% filter(blacknh == 1), models[[11]])
row4[5] <- averagePartialEffect(reg_dat %>% filter(preschool69==1) %>% filter(blacknh == 1), models[[11]])
row5[5] <- averagePartialEffect(reg_dat %>% filter(preschool7072==1) %>% filter(blacknh == 1), models[[11]])
row6[5] <- averagePartialEffect(reg_dat %>% filter(preschool7374==1) %>% filter(blacknh == 1), models[[11]])

row3[6] <- averagePartialEffect(reg_dat %>% filter(preschool6768==1) %>% filter(hispanic == 1), models[[12]])
row4[6] <- averagePartialEffect(reg_dat %>% filter(preschool69==1) %>% filter(hispanic == 1), models[[12]])
row5[6] <- averagePartialEffect(reg_dat %>% filter(preschool7072==1) %>% filter(hispanic == 1), models[[12]])
row6[6] <- averagePartialEffect(reg_dat %>% filter(preschool7374==1) %>% filter(hispanic == 1), models[[12]])

```

```{r}

tab4_df <- rbind(row2, row3, row4, row5, row6)
tab4_df <- round(data.frame(tab4_df), 4)
colnames(tab4_df) <- c('All', 'Boys', 'Girls', 'White, NH', 'Black, NH', 'Hispanic')
rownames(tab4_df) <- c('Preschool post-1969',
                       'Cohort 67-68',
                       'Cohort 69',
                       'Cohort 70-72',
                       'Cohort 73-74')

kable(tab4_df, caption = 'Average partial of treatment for different subpopulations.') %>% kable_classic()
```
Now time to obtain doubly robust estimators for the average treatment effect.
The authors treat the subpopulations separately, and fit separate models for each,
so that's what I will do. I will fit a propensity score model for each subpopulation,
and include exactly the same covariates in that model as I did in the outcome models.

```{r}
# function to make the doubly robust estimators for different datasets
# and models
getDRest <- function(dat, model, prop_score) {
  
  mu1s_dat <- dat %>% mutate(treated = 1)
  mu0s_dat <- dat %>% mutate(treated = 0)
  mu1s <- predict(model, mu1s_dat, type = 'response')
  mu0s <- predict(model, mu0s_dat, type = 'response')
  props <- predict(prop_score, dat, type = 'response')
  trt <- dat %>% select(treated) %>% unlist()
  outcome <- dat %>% select(at_gradelvl) %>% unlist()

  mu1dr <- mean((trt*(outcome - mu1s))/props + mu1s) 
  mu0dr <- mean(((1-trt)*(outcome - mu0s))/(1-props) + mu0s)
  taudr <- mu1dr - mu0dr
  
  return(taudr)

}
```


```{r}
# let's first make the propensity score models (there are 12)
propmods <- vector(mode = 'list', 12)
propmods[[1]] <- glm(treated ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + factor(schoolstart), 
                  family = 'binomial', data = reg_dat)
propmods[[2]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic  + factor(schoolstart), 
                  family = 'binomial', data = reg_dat %>% filter(female == 0))
propmods[[3]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + factor(schoolstart), 
                  family = 'binomial', data = reg_dat %>% filter(female == 1))
propmods[[4]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop + female +
                       momhsgrad + factor(schoolstart), 
                  family = 'binomial', data = reg_dat %>% filter(whitenh == 1))
propmods[[5]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop + female +
                       momhsgrad + factor(schoolstart), 
                  family = 'binomial', data = reg_dat %>% filter(blacknh == 1))
propmods[[6]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop + female +
                       momhsgrad + factor(schoolstart), 
                  family = 'binomial', data = reg_dat %>% filter(hispanic == 1))
propmods[[7]] <- glm(treated ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + factor(schoolstart), 
                  family = 'binomial', data = reg_dat)
propmods[[8]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + factor(schoolstart), 
                  family = 'binomial', data = reg_dat %>% filter(female == 0))
propmods[[9]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + factor(schoolstart), 
                  family = 'binomial', data = reg_dat %>% filter(female == 1))
propmods[[10]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop + female +
                       momhsgrad + factor(schoolstart), 
                  family = 'binomial', data = reg_dat %>% filter(whitenh == 1))
propmods[[11]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop + female +
                       momhsgrad + factor(schoolstart), 
                  family = 'binomial', data = reg_dat %>% filter(blacknh == 1))
propmods[[12]] <- glm(treated ~ hsspend_at_four + fs_available + momhsdrop + female +
                       momhsgrad + factor(schoolstart), 
                  family = 'binomial', data = reg_dat %>% filter(hispanic == 1))
```

```{r}
# pre-allocating the rows
row2 <- rep(0, 6)
row3 <- rep(0, 6)
row4 <- rep(0, 6)
row5 <- rep(0, 6)
row6 <- rep(0, 6)

# getting APE estimates for each group as before
row2[1] <- getDRest(reg_dat %>% filter(preschool1969 == 1), models[[1]], propmods[[1]])
row2[2] <- getDRest(reg_dat %>% filter(preschool1969 == 1) %>% filter(female == 0), models[[2]], propmods[[2]])
row2[3] <- getDRest(reg_dat %>% filter(preschool1969 == 1) %>% filter(female == 1), models[[3]], propmods[[3]])
row2[4] <- getDRest(reg_dat %>% filter(preschool1969 == 1) %>% filter(whitenh == 1), models[[4]], propmods[[4]])
row2[5] <- getDRest(reg_dat %>% filter(preschool1969 == 1) %>% filter(blacknh == 1), models[[5]], propmods[[5]])
row2[6] <- getDRest(reg_dat %>% filter(preschool1969 == 1) %>% filter(blacknh == 1), models[[6]], propmods[[6]])
```

```{r}
row3[1] <- getDRest(reg_dat %>% filter(preschool6768==1), models[[7]], propmods[[7]])
row4[1] <- getDRest(reg_dat %>% filter(preschool69==1), models[[7]], propmods[[7]])
row5[1] <- getDRest(reg_dat %>% filter(preschool7072==1), models[[7]], propmods[[7]])
row6[1] <- getDRest(reg_dat %>% filter(preschool7374==1), models[[7]], propmods[[7]])

row3[2] <- getDRest(reg_dat %>% filter(preschool6768==1) %>% filter(female == 0), models[[8]], propmods[[8]])
row4[2] <- getDRest(reg_dat %>% filter(preschool69==1) %>% filter(female == 0), models[[8]], propmods[[8]])
row5[2] <- getDRest(reg_dat %>% filter(preschool7072==1) %>% filter(female == 0), models[[8]], propmods[[8]])
row6[2] <- getDRest(reg_dat %>% filter(preschool7374==1) %>% filter(female == 0), models[[8]], propmods[[8]])

row3[3] <- getDRest(reg_dat %>% filter(preschool6768==1) %>% filter(female == 1), models[[9]], propmods[[9]])
row4[3] <- getDRest(reg_dat %>% filter(preschool69==1) %>% filter(female == 1), models[[9]], propmods[[9]])
row5[3] <- getDRest(reg_dat %>% filter(preschool7072==1) %>% filter(female == 1), models[[9]], propmods[[9]])
row6[3] <- getDRest(reg_dat %>% filter(preschool7374==1) %>% filter(female == 1), models[[9]], propmods[[9]])

row3[4] <- getDRest(reg_dat %>% filter(preschool6768==1) %>% filter(whitenh == 1), models[[10]],propmods[[10]])
row4[4] <- getDRest(reg_dat %>% filter(preschool69==1) %>% filter(whitenh == 1), models[[10]],propmods[[10]])
row5[4] <- getDRest(reg_dat %>% filter(preschool7072==1) %>% filter(whitenh == 1), models[[10]],propmods[[10]])
row6[4] <- getDRest(reg_dat %>% filter(preschool7374==1) %>% filter(whitenh == 1), models[[10]], propmods[[10]])

row3[5] <- getDRest(reg_dat %>% filter(preschool6768==1) %>% filter(blacknh == 1), models[[11]],propmods[[11]])
row4[5] <- getDRest(reg_dat %>% filter(preschool69==1) %>% filter(blacknh == 1), models[[11]],propmods[[11]])
row5[5] <- getDRest(reg_dat %>% filter(preschool7072==1) %>% filter(blacknh == 1), models[[11]], propmods[[11]])
row6[5] <- getDRest(reg_dat %>% filter(preschool7374==1) %>% filter(blacknh == 1), models[[11]], propmods[[11]])

row3[6] <- getDRest(reg_dat %>% filter(preschool6768==1) %>% filter(hispanic == 1), models[[12]],propmods[[12]])
row4[6] <- getDRest(reg_dat %>% filter(preschool69==1) %>% filter(hispanic == 1), models[[12]], propmods[[12]])
row5[6] <- getDRest(reg_dat %>% filter(preschool7072==1) %>% filter(hispanic == 1), models[[12]], propmods[[12]])
row6[6] <- getDRest(reg_dat %>% filter(preschool7374==1) %>% filter(hispanic == 1), models[[12]], propmods[[12]])
```

```{r}

tab4_df <- rbind(row2, row3, row4, row5, row6)
tab4_df <- round(data.frame(tab4_df), 4)
colnames(tab4_df) <- c('All', 'Boys', 'Girls', 'White, NH', 'Black, NH', 'Hispanic')
rownames(tab4_df) <- c('Preschool post-1969',
                       'Cohort 67-68',
                       'Cohort 69',
                       'Cohort 70-72',
                       'Cohort 73-74')

kable(tab4_df, caption = 'Doubly robust estimate of treatment for different subpopulations.') %>% kable_classic()
```
Results that we observed before is confirmed for the doubly robust estimator!




