---
title: "1990 Outcome Results"
output: pdf_document
---

```{r}
library(rstudioapi)
library(haven)
library(dplyr)
library(ggplot2)
library(readr)
library(measurements)
library(geosphere)
library(tidyr)
library(kableExtra)
```

```{r}
# load data
raw_path <- paste0(dirname(getSourceEditorContext()$path), '/data/raw/')
processed_path <- paste0(dirname(getSourceEditorContext()$path), '/data/processed/')
census1990 <- readRDS(paste0(processed_path, 'census1990_clean.Rda'))

# add schoolstart column to be birthyr + 6 (since birth quarter information not available)
census1990 <- census1990 %>% mutate(schoolstart = birthyr+6)
```

# Replicating the Version of Figure 5, but for Each Outcome

```{r}
avg_cov <- mean(census1990$pred_cov)
low_cov <- census1990 %>% filter(pred_cov <= avg_cov) %>% group_by(schoolstart) %>% summarize(prop_nohsgrad = mean(no_hsgrad), prop_onlyhsgrad = mean(only_hsgrad), prop_anycoll = mean(any_college))
high_cov <- census1990 %>% filter(pred_cov > avg_cov) %>% group_by(schoolstart) %>% summarize(prop_nohsgrad = mean(no_hsgrad), prop_onlyhsgrad = mean(only_hsgrad), prop_anycoll = mean(any_college))

low_cov <- gather(low_cov, key = 'category', value = 'low_prop', prop_nohsgrad, prop_onlyhsgrad, prop_anycoll)
high_cov <- gather(high_cov, key = 'category', value = 'high_prop', prop_nohsgrad, prop_onlyhsgrad, prop_anycoll)
cov_comparison <- low_cov %>% mutate(high_prop = high_cov$high_prop)
```


```{r}
ggplot(cov_comparison) + geom_col(aes(x = as.factor(schoolstart), y = high_prop-low_prop, fill = category)) + xlab('Expected Year of Beginning School') + ylab('Difference in Proportions of \n Educational Attainment') + ggtitle('Comparing Proportions of Educational Attainment, High vs. Low Coverage') + theme_light() + scale_fill_discrete(name = '', labels = c('Any College', 'Only HS Grad', 'No HS Grad'))

```

Doesn't really seem like there are any important effects here. In general seems like
the difference in proportions of people that attended college actually marginally goes
down, no effect. Seems like there may be differences in areas with high coverage and low
coverage, but it doesn't change for who would have been exposed to Sesame Street.

# Fitting Regression Models

```{r}
# Subsetting proper data for model fitting

reg_dat <- census1990 %>% select(hsspend_at_four, fs_available, female, 
                                 blacknh, othernh, hispanic, 
                                 full_cty_fips, st_fips, schoolstart, 
                                 preschool1969, pred_cov, no_hsgrad, 
                                 only_hsgrad, any_college, whitenh)
```

## Model 1: As Close to Their Model 1 As Possible No Fixed Effects

Mainly trying to replicate first two rows of Table 6

```{r}
# pre-allocating the rows of Table 4
row1 <- rep(0, 3)
row2 <- rep(0, 3)
row3 <- rep(0, 3)
row4 <- rep(0, 3)
row5 <- rep(0, 3)
row6 <- rep(0, 3)
```


```{r}
# filling in the first row of the means of at-grade level students
row1[1] <- mean(reg_dat$no_hsgrad)
row1[2] <- mean(reg_dat$only_hsgrad)
row1[3] <- mean(reg_dat$any_college)
```

Next several chunks are all about fitting the regression models to create the second row
of Table 4. Note we don't bother with any of the fixed effects.

```{r}
# takes really long to fit all of the fixed effects (county level + state x birth cohort)
# starting with just not fitting the fixed effects
logistic_mod1 <- glm(no_hsgrad ~ hsspend_at_four + fs_available + female + blacknh + 
                       othernh + hispanic + preschool1969:pred_cov, 
                     family = 'binomial', data = reg_dat)
row2[1] <- as.numeric(logistic_mod1$coefficients['preschool1969:pred_cov'])
```

```{r}
logistic_mod1 <- glm(only_hsgrad ~ hsspend_at_four + fs_available + blacknh + 
                       othernh + hispanic + preschool1969:pred_cov, 
                     family = 'binomial', data = reg_dat)
row2[2] <- as.numeric(logistic_mod1$coefficients['preschool1969:pred_cov'])
```

```{r}
logistic_mod1 <- glm(any_college ~ hsspend_at_four + fs_available + blacknh + 
                       othernh + hispanic + preschool1969:pred_cov, 
                     family = 'binomial', data = reg_dat)
row2[3] <- as.numeric(logistic_mod1$coefficients['preschool1969:pred_cov'])
```

## Model 2: As Close to Their Model 2, No Extra Fixed Effects

Next code is to replicate the next four rows of Table 6.

```{r}
reg_dat <- reg_dat %>% mutate(preschool6768 = as.integer(reg_dat$schoolstart >= 1967 & reg_dat$schoolstart <= 1968)) %>%
  mutate(preschool69 = as.integer(reg_dat$schoolstart == 1969)) %>%
  mutate(preschool7072 = as.integer(reg_dat$schoolstart >= 1970 & reg_dat$schoolstart <= 1972)) %>%
  mutate(preschool7374 = as.integer(reg_dat$schoolstart >= 1973 & reg_dat$schoolstart <= 1974))

logistic_mod2 <- glm(no_hsgrad ~ hsspend_at_four + fs_available + female + blacknh + 
                       othernh + hispanic + preschool6768:pred_cov + 
                       preschool69:pred_cov + preschool7072:pred_cov + preschool7374:pred_cov, 
                     family = 'binomial', data = reg_dat)

row3[1] <- as.numeric(logistic_mod2$coefficients['preschool6768:pred_cov'])
row4[1] <- as.numeric(logistic_mod2$coefficients['pred_cov:preschool69'])
row5[1] <- as.numeric(logistic_mod2$coefficients['pred_cov:preschool7072'])
row6[1] <- as.numeric(logistic_mod2$coefficients['pred_cov:preschool7374'])
```

```{r}
logistic_mod2 <- glm(only_hsgrad ~ hsspend_at_four + fs_available + blacknh + 
                       othernh + hispanic + preschool6768:pred_cov + 
                       preschool69:pred_cov + preschool7072:pred_cov + preschool7374:pred_cov, 
                     family = 'binomial', data = reg_dat)

row3[2] <- as.numeric(logistic_mod2$coefficients['preschool6768:pred_cov'])
row4[2] <- as.numeric(logistic_mod2$coefficients['pred_cov:preschool69'])
row5[2] <- as.numeric(logistic_mod2$coefficients['pred_cov:preschool7072'])
row6[2] <- as.numeric(logistic_mod2$coefficients['pred_cov:preschool7374'])
```

```{r}
logistic_mod2 <- glm(any_college ~ hsspend_at_four + fs_available + blacknh + 
                       othernh + hispanic + preschool6768:pred_cov + 
                       preschool69:pred_cov + preschool7072:pred_cov + preschool7374:pred_cov, 
                     family = 'binomial', data = reg_dat)

row3[3] <- as.numeric(logistic_mod2$coefficients['preschool6768:pred_cov'])
row4[3] <- as.numeric(logistic_mod2$coefficients['pred_cov:preschool69'])
row5[3] <- as.numeric(logistic_mod2$coefficients['pred_cov:preschool7072'])
row6[3] <- as.numeric(logistic_mod2$coefficients['pred_cov:preschool7374'])
```

```{r}
# making Table 4, but only giving the coefficients of the logit model

tab6_df <- rbind(row1, row2, row3, row4, row5, row6)
tab6_df <- round(data.frame(tab6_df), 4)
colnames(tab6_df) <- c('HS dropout', 'HS graduate', 'Any college')
rownames(tab6_df) <- c('Proportion of:', 
                       'Preschool post-1969 x coverage rate',
                       'Coverage rate x 67-68',
                       'Coverage rate x 69',
                       'Coverage rate x 70-72',
                       'Coverage rate x 73-74')

kable(tab6_df, caption = 'Logistic regression coefficients of variable capturing causal effect of interest for different subgroups.') %>% kable_classic()
```

```{r}
# making Table 4, but multiplying by 30 percentage points and exponentiating to get the
# factorial increase in odds of being at grade-level

tab6_df <- rbind(row2, row3, row4, row5, row6)
tab6_df <- round(exp(data.frame(tab6_df)*30), 2)
colnames(tab6_df) <- c('HS dropout', 'HS graduate', 'Any college')
rownames(tab6_df) <- c('Preschool post-1969 x coverage rate',
                       'Coverage rate x 67-68',
                       'Coverage rate x 69',
                       'Coverage rate x 70-72',
                       'Coverage rate x 73-74')

kable(tab6_df, caption = 'Odds ratio of outcomes when SS coverage is increased by 30 percentage points') %>% kable_classic()
```

Seems like there is no effect..


