---
title: "outcome regression 2000"
output: pdf_document
---

```{r}
library(rstudioapi)
library(haven)
library(dplyr)
library(ggplot2)
library(readr)
library(measurements)
library(geosphere)
library(tidyr)
```

```{r}
raw_path <- paste0(dirname(getSourceEditorContext()$path), '/data/raw/')
processed_path <- paste0(dirname(getSourceEditorContext()$path), '/data/processed/')

# get vector of char widths for each column (taken from authors STATA code)
widths2000 <- c(4-1, 6-5, 14-7, 24-15, 26-25, 30-27, 0, 35-32, 45-36, 
                47-46, 0, 51-49, 55-52, 0, 59-57, 0, 63-61, 66-64, 71-67, 75-72, 
                77-76, 81-78, 0, 84-83, 87-85, 0, 90-89, 92-91, 94-93, 100-95, 
                105-101, 108-106, 111-109)
widths2000 <- widths2000 + 1
# get vector of column names (taken from authors STATA code)
names2000 <- c('year', 'datanum', 'serial', 'hhwt', 'statefip', 'county', 'gq', 
               'pernum', 'perwt', 'momloc', 'sex', 'age', 'birthyr', 
               'race', 'raced', 'hispan', 'hispand', 'bpl', 'bpld', 'yrimmig', 
               'language', 'languaged', 'speakeng', 
               'educ', 'educd', 'empstat', 'empstatd', 'wkswork1', 'uhrswork', 
               'incwage', 'incwelfr', 'poverty', 'migplac5')
# read in the data
census2000 <- read_fwf(file=paste0(raw_path, 'census2000.dat'), 
                       col_positions=fwf_widths(widths2000, names2000))
```

Once again largely lifting the preprocessing code from the 1980 census, except
leaving the mother's educational status behind since, according to the paper,
they can't get that from the data. I guess it makes sense that mothers can't be identified
since a lot of these people in 1990 and 2000 would be moving out.

```{r}
# subset by birth year to get the children
census2000 <- filter(census2000, birthyr>=1959 & birthyr <= 1968)

# get rid of all individuals who have missing county info (can't be matched to a coverage)
census2000$cnty_fips <- as.numeric(census2000$county)/10
census2000 <- census2000 %>% filter(cnty_fips != 0)
census2000$cnty_fips <- sprintf("%03s", census2000$cnty_fips)

# Subset to not include kids who moved from birth state
# Birth state is in census as 'bpl', so we can compare to current state to see if they moved.
# migplac5 is state lived in in 1975, could also use this as an alternative to what the paper did
# (maybe compare birth state with state in 1975 with state in 2000?)
census2000 <- census2000[sprintf("%03s", census2000$statefip) == census2000$bpl,]
census2000 <- census2000 %>% rename(st_fips = statefip)
```

```{r}
census_counties <- census2000 %>% 
  group_by(st_fips, cnty_fips) %>%
  select(st_fips, cnty_fips) %>%
  unique() %>% 
  ungroup()

census_counties$pred_cov <- sapply(1:nrow(census_counties), function(i) {
  row <- SSstation_cty_final %>%
    filter(stfips_hh==census_counties$st_fips[i]) %>%
    filter(ctyfips_hh==census_counties$cnty_fips[i])
  if (nrow(row)==1) {
    return(row[["max_pred_cov"]])
  } else {
    return(NA)
  }
})
#### seems like we're losing a lot of data, why? ####

# Add pred_cov by joining census_counties and census2000 on st_fips and cnty_fips
#df <- select(census2000, serial, cnty_fips, st_fips)
census2000 <- inner_join(census2000, census_counties, by = c("cnty_fips", "st_fips"))

# Subset to only include counties for which coverage is known
census2000 <- na.omit(census2000)

```

```{r}
# put in food stamp indicators
fs_background <- read_dta(paste0(raw_path, 'fs_background.dta')) %>% 
  select(cnty_fips=countyfips, st_fips=stfips, fs_year)
fs_background$cnty_fips <- sprintf("%03d", fs_background$cnty_fips)
fs_background$st_fips <- sprintf("%02d", fs_background$st_fips)
census2000 <- inner_join(census2000, fs_background, by = c("cnty_fips", "st_fips"))

# For kid's county, was birth year + 6 >= year food stamps were introduced
census2000 <- census2000 %>% 
  group_by(cnty_fips, st_fips) %>% 
  mutate(fs_available = as.integer(birthyr + 6 >= fs_year)) %>%
  ungroup()
```

```{r}
census2000$fs_available[is.na(census2000$fs_available)] = 0
```

Add Head Start Spending info

```{r}
hsspend <- read_dta(paste0(raw_path, "ludwig_miller_HSspend.dta"))

# This dataset contains better FIPS coding (state and county column)
recode <- read_dta(paste0(raw_path, "ludwig_miller_fipsrecode.dta"))
recode$state <- sprintf('%02s', recode$state)
recode$county <- sprintf('%03s', recode$county)
hsspend_df <- na.omit(inner_join(hsspend, recode, by="oldcode"))

hsspend_df <- hsspend_df %>%
  rename(hsspend68 = qje68) %>%
  rename(hsspend72 = qje72a) %>% # a used in .log
  mutate(hsspend69 = hsspend68 + (hsspend72-hsspend68)/4) %>%
  mutate(hsspend70 = hsspend68 + (hsspend72-hsspend68)/2) %>%
  mutate(hsspend71 = hsspend68 + 3*(hsspend72-hsspend68)/4) %>%
  rename(st_fips = state) %>%
  rename(cnty_fips = county) %>%
  select(-c("qje72b", "qje72c", "pop70", "oldcode"))

# Include HS expenditures in county for kid at age 4 in census dataset
# cfips90 column of census2000 is FIPS code of <state, county> combo
census2000 <- inner_join(census2000, hsspend_df, by = c("cnty_fips", "st_fips"))
census2000$hsspend_at_four <- rep(0, nrow(census2000))
idx <- which(census2000$birthyr==1964)
census2000$hsspend_at_four[idx] <- census2000$hsspend68[idx]
idx <- which(census2000$birthyr==1965)
census2000$hsspend_at_four[idx] <- census2000$hsspend69[idx]
idx <- which(census2000$birthyr==1966)
census2000$hsspend_at_four[idx] <- census2000$hsspend70[idx]
idx <- which(census2000$birthyr==1967)
census2000$hsspend_at_four[idx] <- census2000$hsspend71[idx]
idx <- which(census2000$birthyr==1968)
census2000$hsspend_at_four[idx] <- census2000$hsspend72[idx]
```

```{r}
# other non hispanic and black non hispanic
census2000$othernh <- as.integer(census2000$race != 1 & census2000$race != 0 & census2000$hispan == 0)
census2000$blacknh <- as.integer(census2000$race == 2 & census2000$hispan == 0)
census2000$hispanic <- as.integer(census2000$hispan > 0)
census2000$female <- as.integer(census2000$sex == 2)
```

In the 1990 and 2000 censuses, there is no `birthqtr` column, so we can't determine
more precisely when they started school and consequently when they would have left pre-k.
The authors just decide that an individual is was in preschool in 1969 if the year
they turned 6 (i.e. should have started first grade) is after 1969. Note how this
contrasts with the 1980 data, where an individual was in preschool in 1969 if their
expected start year of first grade based on their state school entry laws/cutoffs
was after 1969. 

```{r}
# Column for whether preschool age, per paper
census2000$preschool1969 <- as.integer(census2000$birthyr + 6 > 1969)
census2000 <- census2000 %>% mutate(preschool_cov = census2000$preschool1969*census2000$pred_cov)
```

Now, let's do some cleaning to make the outcome variables.

```{r}
# drop individuals who don't have their income as a percentage of the poverty rate
census2000 <- census2000[census2000$poverty != '000',]
# drop individuals who don't have an employment status listed (I think this is actually 0)
census2000 <- census2000[census2000$empstat != 0,]

# cleaning for hourly wages is a little bit more complicated
# unclear exactly what the paper does (seems to compute regardless of missingess and fillNA for <1 and >1000 hrly wages..)
# I think this basically amounts to computing the hourly wages as normal and then dropping
# observations for which the hourly wages are either too high or missing

census2000$hourly_wages <- as.integer(census2000$incwage)/(as.integer(census2000$uhrswork) * as.integer(census2000$wkswork1))
# drop any obs for which wages could not be computed
census2000 <- census2000[is.na(census2000$hourly_wages),]
# filter according to the papers specs mentioned above
census2000 <- census2000 %>% filter(hourly_wages >= 1, hourly_wages <= 1000)
```

```{r}
# add the other two outcomes: poverty and employment

# individual is in poverty if income is a fraction of the poverty line
census2000$in_poverty <- as.integer(census2000$poverty < '100')

# whether or not individual is currently employed
census2000$is_working <- as.integer(census2000$empstat == 1)

# calculating log hourly wages



```

```{r}
nrow(census2000 %>% filter(empstat == 1, wkswork1 == '00'))
```

