---
title: "outcome regression 1990"
output: html_document
---

```{r}
library(rstudioapi)
library(haven)
library(dplyr)
library(ggplot2)
library(readr)
library(measurements)
library(geosphere)
library(tidyr)
```

```{r}
raw_path <- paste0(dirname(getSourceEditorContext()$path), '/data/raw/')
processed_path <- paste0(dirname(getSourceEditorContext()$path), '/data/processed/')

# get vector of char widths for each column (taken from authors STATA code)
widths1990 <- c(4-1, 6-5, 14-7, 24-15, 26-25, 30-27, 0, 35-32, 45-36, 
                47-46, 0, 51-49, 55-52, 0, 59-57, 0, 63-61, 66-64, 71-67, 75-72, 
                77-76, 81-78, 0, 0, 85-84, 88-86, 0, 91-90, 93-92, 95-94, 101-96, 
                106-102, 109-107, 112-110)
widths1990 <- widths1990 + 1
# get vector of column names (taken from authors STATA code)
names1990 <- c('year', 'datanum', 'serial', 'hhwt', 'statefip', 'county', 'gq', 
               'pernum', 'perwt', 'momloc', 'sex', 'age', 'birthyr', 
               'race', 'raced', 'hispan', 'hispand', 'bpl', 'bpld', 'yrimmig', 
               'language', 'languaged', 'speakeng', 'school', 
               'educ', 'educd', 'empstat', 'empstatd', 'wkswork1', 'uhrswork', 
               'incwage', 'incwelfr', 'poverty', 'migplac5')
# read in the data
census1990 <- read_fwf(file=paste0(raw_path, 'census1990.dat'), 
                       col_positions=fwf_widths(widths1990, names1990))

# load all relevant datasets
SSstation_cty_final <- readRDS(paste0(processed_path, "SScoverage.Rda"))
```
We can largely lift the preprocessing from what we did for the 1980 Census data.
Only thing to do is to refashion the outcome, but we don't need to deal with
the mother's education stuff since, according to the authors, they can only
get that info from the 1990 census (not sure why they can't get it from there?)

```{r}
# subset by birth year to get the children
census1990 <- filter(census1990, birthyr>=1959 & birthyr <= 1968)

# get rid of all individuals who have missing county info (can't be matched to a coverage)
census1990$cnty_fips <- as.numeric(census1990$county)/10
census1990 <- census1990 %>% filter(cnty_fips != 0)
census1990$cnty_fips <- sprintf("%03s", census1990$cnty_fips)

# Subset to not include kids who moved from birth state
# Birth state is in census as 'bpl', so we can compare to current state to see if they moved.
# migplac5 is state lived in in 1975, could also use this as an alternative to what the paper did
# (maybe compare birth state with state in 1975 with state in 1990?)
census1990 <- census1990[sprintf("%03s", census1990$statefip) == census1990$bpl,]
census1990 <- census1990 %>% rename(st_fips = statefip)
```

```{r}
census_counties <- census1990 %>% 
  group_by(st_fips, cnty_fips) %>%
  select(st_fips, cnty_fips) %>%
  unique() %>% 
  ungroup()

census_counties$pred_cov <- sapply(1:nrow(census_counties), function(i) {
  row <- SSstation_cty_final %>%
    filter(stfips_hh==census_counties$st_fips[i]) %>%
    filter(ctyfips_hh==census_counties$cnty_fips[i])
  if (nrow(row)==1) {
    return(row[["max_pred_cov"]])
  } else {
    return(NA)
  }
})
#### seems like we're losing a lot of data, why? ####

# Add pred_cov by joining census_counties and census1990 on st_fips and cnty_fips
#df <- select(census1990, serial, cnty_fips, st_fips)
census1990 <- inner_join(census1990, census_counties, by = c("cnty_fips", "st_fips"))

# Subset to only include counties for which coverage is known
census1990 <- na.omit(census1990)

```

```{r}
# put in food stamp indicators
fs_background <- read_dta(paste0(raw_path, 'fs_background.dta')) %>% 
  select(cnty_fips=countyfips, st_fips=stfips, fs_year)
fs_background$cnty_fips <- sprintf("%03d", fs_background$cnty_fips)
fs_background$st_fips <- sprintf("%02d", fs_background$st_fips)
census1990 <- inner_join(census1990, fs_background, by = c("cnty_fips", "st_fips"))

# For kid's county, was birth year + 6 >= year food stamps were introduced
census1990 <- census1990 %>% 
  group_by(cnty_fips, st_fips) %>% 
  mutate(fs_available = as.integer(birthyr + 6 >= fs_year)) %>%
  ungroup()
```

Note: there are some individuals missing their foodstamp info, in counties 09150 and 09130.
For some reason, there are several counties that don't have foodstamp years (about 10 out of 3000).
Let's assume for these counties that there was no foodstamp program implemented (at least in that particular timeframe)
and so all those individuals should have '0' for food stamp availability.

```{r}
census1990$fs_available[is.na(census1990$fs_available)] = 0
```

Add Head Start Spending info

```{r}
hsspend <- read_dta(paste0(raw_path, "ludwig_miller_HSspend.dta"))

# This dataset contains better FIPS coding (state and county column)
recode <- read_dta(paste0(raw_path, "ludwig_miller_fipsrecode.dta"))
recode$state <- sprintf('%02s', recode$state)
recode$county <- sprintf('%03s', recode$county)
hsspend_df <- na.omit(inner_join(hsspend, recode, by="oldcode"))

hsspend_df <- hsspend_df %>%
  rename(hsspend68 = qje68) %>%
  rename(hsspend72 = qje72a) %>% # a used in .log
  mutate(hsspend69 = hsspend68 + (hsspend72-hsspend68)/4) %>%
  mutate(hsspend70 = hsspend68 + (hsspend72-hsspend68)/2) %>%
  mutate(hsspend71 = hsspend68 + 3*(hsspend72-hsspend68)/4) %>%
  rename(st_fips = state) %>%
  rename(cnty_fips = county) %>%
  select(-c("qje72b", "qje72c", "pop70", "oldcode"))

# Include HS expenditures in county for kid at age 4 in census dataset
# cfips90 column of census1990 is FIPS code of <state, county> combo
census1990 <- inner_join(census1990, hsspend_df, by = c("cnty_fips", "st_fips"))
census1990$hsspend_at_four <- rep(0, nrow(census1990))
idx <- which(census1990$birthyr==1964)
census1990$hsspend_at_four[idx] <- census1990$hsspend68[idx]
idx <- which(census1990$birthyr==1965)
census1990$hsspend_at_four[idx] <- census1990$hsspend69[idx]
idx <- which(census1990$birthyr==1966)
census1990$hsspend_at_four[idx] <- census1990$hsspend70[idx]
idx <- which(census1990$birthyr==1967)
census1990$hsspend_at_four[idx] <- census1990$hsspend71[idx]
idx <- which(census1990$birthyr==1968)
census1990$hsspend_at_four[idx] <- census1990$hsspend72[idx]
```

```{r}
# other non hispanic and black non hispanic
census1990$othernh <- as.integer(census1990$race != 1 & census1990$race != 0 & census1990$hispan == 0)
census1990$blacknh <- as.integer(census1990$race == 2 & census1990$hispan == 0)
census1990$hispanic <- as.integer(census1990$hispan > 0)
census1990$female <- as.integer(census1990$sex == 2)
```

In the 1990 and 2000 censuses, there is no `birthqtr` column, so we can't determine
more precisely when they started school and consequently when they would have left pre-k.
The authors just decide that an individual is was in preschool in 1969 if the year
they turned 6 (i.e. should have started first grade) is after 1969. Note how this
contrasts with the 1980 data, where an individual was in preschool in 1969 if their
expected start year of first grade based on their state school entry laws/cutoffs
was after 1969. 

```{r}
# Column for whether preschool age, per paper
census1990$preschool1969 <- as.integer(census1990$birthyr + 6 > 1969)
census1990 <- census1990 %>% mutate(preschool_cov = census1990$preschool1969*census1990$pred_cov)
```

Now, let's make the outcome variables: not a high school graduate, only a high school graduate (and no higher), and attending any college.

```{r}
# we have 3 outcomes: not a high school grad, only high school graduate, and attending any college
census1990 <- census1990 %>% mutate(no_hsgrad = as.integer(census1990$educd < '062'))
census1990 <- census1990 %>% mutate(only_hsgrad = as.integer(census1990$educd == '062'))
census1990 <- census1990 %>% mutate(any_college = as.integer(census1990$educd > '062'))
```

```{r}
#save the data
saveRDS(census1990, file=paste0(processed_path, 'census1990_clean.Rda'))
```