---
title: "outcome regression"
output: html_document
date: "2022-12-05"
---

```{r}
library(rstudioapi)
library(haven)
library(dplyr)
library(ggplot2)
library(readr)
library(measurements)
library(geosphere)
library(tidyr)
```


```{r}
raw_path <- paste0(dirname(getSourceEditorContext()$path), '/data/raw/')
processed_path <- paste0(dirname(getSourceEditorContext()$path), '/data/processed/')

# load all relevant datasets
SSstation_cty_final <- readRDS(paste0(processed_path, "SScoverage.Rda"))
school_cutoffs <- read_dta(paste0(raw_path, "school_cutoffs.dta"))

widths1980 <- c(4-1, 6-5, 14-7, 24-15, 26-25, 30-27, 0, 35-32, 45-36, 
                47-46, 0, 51-49, 0, 56-53, 0, 60-58, 0, 64-62, 67-65,
                72-68, 76-73, 78-77, 82-79, 0, 0, 86-85, 89-87, 91-90, 94-92, 0, 
                97-96, 100-98, 103-101, 0, 0)
widths1980 <- widths1980 + 1
# get vector of column names (taken from authors STATA code)
names1980 <- c('year', 'datanum', 'serial', 'hhwt', 'statefip', 'county', 'gq', 
               'pernum', 'perwt', 'momloc', 'sex', 'age', 'birthqtr', 'birthyr', 
               'race', 'raced', 'hispan', 'hispand', 'bpl', 'bpld', 'yrimmig', 
               'language', 'languaged', 'speakeng', 'school', 
               'higrade', 'higraded', 'educ', 'educd', 'gradeatt', 'gradeattd', 
               'migplac5', 'migcogrp', 'samemet5', 'migsamp')
# read in the data
census1980 <- read_fwf(file=paste0(raw_path, 'census1980.dat'), 
                       col_positions=fwf_widths(widths1980, names1980))
```

Columns we need to fit model 1:
- whether in preschool in 1969 (done: preschool1969 i.e. born in 1964-1968, I think)
- coverage rate of a kid's county (done)
    - for this, need to link counties in SSstation_cty_final (FIPS for state + county) with 1980 census
    - I think these are FIPS with a 0 at the end
    - Put in the predicted coverage given these FIPS codes
- policy (done: hsspend_at_four and fs_available)
    - HeadStart expenditures for kid at 4 and food stamps indicator for kid at 6
- demographic characteristics:
    - race, ethnicity, gender, mother's level of education, indicator for mother being present in house at time of census
- outcome: grade-for-age status
    - TO DO: calculate
- state (done: st_fips)
- cohort (done: preschool1969 for model 1, I think)
- county (done: cfips90)

Basic exploration

```{r}
# # 106 county codes. Re-use same codes for different states? Texas alone has >250...
# length(unique(census1980$county))
# 
# # census uses 50 states + DC; only predict coverage in 49 states (in SSstation_cty_covs)
# length(unique(census1980$statefip))
# length(unique(SSstation_cty_final$stname))
# 
# # Comparing county codes
# sort(unique(census1980$county))
# sort(unique(SSstation_cty_final$ctyfips_hh))
# 
# colnames(census1980)
```

Before we start subsetting the relevant children for the analysis, we need to grab
the information about the mothers (education level, etc.).

Supposed to use info from `pernum` and `serial`.
`pernum`: uniquely specifies a member of a household within a household
`serial`: uniquely identifies a household (so along with `pernum`, uniquely IDs person)
`momloc`: if 0, mother not present, otherwise gives the `pernum` of the mother in the house

I think they use three mother-related variables: whether mother was a high-school dropout,
whether mother only graduated high school, and whether the child lives with the mother.
It seems that the mother education variables are set to zero if the child does not
live with the mother.

```{r}
poss_mothers <- census1980 %>% filter(birthyr < 1959)
poss_mothers <- poss_mothers %>% select(datanum, serial, pernum, educd) %>% rename(momid = pernum)

# generate columns for mothers who did not finish high school, and who only finished high
# school but no more educational attainment
poss_mothers <- poss_mothers %>% mutate(momhsgrad = as.integer(as.integer(poss_mothers$educd) == 60)) %>%
  mutate(momhsdrop = as.integer(as.integer(poss_mothers$educd) < 60))

# subset by birth year to get the children
census1980 <- filter(census1980, birthyr>=1959 & birthyr <= 1968) %>% rename(momid = momloc)
census1980$momid <- sprintf('%04s', census1980$momid)
census1980 <- left_join(x=census1980, y=poss_mothers, by = c('datanum', 'serial', 'momid'))
# drop observations who didn't have mothers to match in the dataset but are listed as having moms present
census1980 <- census1980[!(is.na(census1980$momhsgrad) & census1980$momid != '0000'),]
# indicator for only hs grad AND mother present
census1980$momhsgrad <- census1980$momhsgrad %>% replace_na(0)
# indicator for less than hs AND mother present
census1980$momhsdrop <- census1980$momhsdrop %>% replace_na(0)
# indicator if you live with your mom
census1980$livwmom <- as.integer(census1980$momid != '0000')
```

Now start subsetting the children once we have the mother information.

```{r}
# get rid of all individuals who have missing county info (can't be matched to a coverage)
census1980$cnty_fips <- as.numeric(census1980$county)/10
census1980 <- census1980 %>% filter(cnty_fips != 0)
census1980$cnty_fips <- sprintf("%03s", census1980$cnty_fips)

# Subset to not include kids who moved from birth state
# Birth state is in census as 'bpl', so we can compare to current state to see if they moved.
# migplac5 is state lived in in 1975, could also use this as an alternative to what the paper did
# (maybe compare birth state with state in 1975 with state in 1980?)
census1980 <- census1980[sprintf("%03s", census1980$statefip) == census1980$bpl,]
census1980 <- census1980 %>% rename(st_fips = statefip)

#stuff with migplac5
#census1980$st_fips_1975 <- as.integer(census1980$migplac5)
#census1980$st_fips <- as.integer(census1980$statefip)
#census1980 <- filter(census1980, st_fips==st_fips_1975)

# Has to live in a state (between 1 and 56) in past and present
#census1980 <- filter(census1980, st_fips_1975 >= 1 & st_fips_1975 <= 56)
#census1980 <- filter(census1980, st_fips >= 1 & st_fips <= 56)
```


Put in each kid's Sesame Street coverage rate. 
Remove samples of counties with unknown coverage.

Pseudocode:
For each grouping of (ctyfips_hh, stfips_hh) in census1980:
  if it's in SSstation_cty_final, return its max_pred_cov. Else, return NA
Then join resulting vector into census1980 by (ctyfips_hh, stfips_hh)


```{r}
census_counties <- census1980 %>% 
  group_by(st_fips, cnty_fips) %>%
  select(st_fips, cnty_fips) %>%
  unique() %>% 
  ungroup()

census_counties$pred_cov <- sapply(1:nrow(census_counties), function(i) {
  row <- SSstation_cty_final %>%
    filter(stfips_hh==census_counties$st_fips[i]) %>%
    filter(ctyfips_hh==census_counties$cnty_fips[i])
  if (nrow(row)==1) {
    return(row[["max_pred_cov"]])
  } else {
    return(NA)
  }
})

# Add pred_cov by joining census_counties and census1980 on st_fips and cnty_fips
#df <- select(census1980, serial, cnty_fips, st_fips)
census1980 <- inner_join(census1980, census_counties, by = c("cnty_fips", "st_fips"))

# Subset to only include counties for which coverage is known
census1980 <- na.omit(census1980)
```

Put Food Stamp indicator in census1980. Did the kid at age 6 have access in the county to food stamps?

```{r}
fs_background <- read_dta(paste0(raw_path, 'fs_background.dta')) %>% 
  select(cnty_fips=countyfips, st_fips=stfips, fs_year)
fs_background$cnty_fips <- sprintf("%03d", fs_background$cnty_fips)
fs_background$st_fips <- sprintf("%02d", fs_background$st_fips)
census1980 <- inner_join(census1980, fs_background, by = c("cnty_fips", "st_fips"))

# For kid's county, was birth year + 6 >= year food stamps were introduced
census1980 <- census1980 %>% 
  group_by(cnty_fips, st_fips) %>% 
  mutate(fs_available = as.integer(birthyr + 6 >= fs_year)) %>%
  ungroup()
```



Put Head Start expenditures in census1980.

```{r}
hsspend <- read_dta(paste0(raw_path, "ludwig_miller_HSspend.dta"))

# This dataset contains better FIPS coding (state and county column)
recode <- read_dta(paste0(raw_path, "ludwig_miller_fipsrecode.dta"))
recode$state <- sprintf('%02s', recode$state)
recode$county <- sprintf('%03s', recode$county)
hsspend_df <- na.omit(inner_join(hsspend, recode, by="oldcode"))

hsspend_df <- hsspend_df %>%
  rename(hsspend68 = qje68) %>%
  rename(hsspend72 = qje72a) %>% # a used in .log
  mutate(hsspend69 = hsspend68 + (hsspend72-hsspend68)/4) %>%
  mutate(hsspend70 = hsspend68 + (hsspend72-hsspend68)/2) %>%
  mutate(hsspend71 = hsspend68 + 3*(hsspend72-hsspend68)/4) %>%
  rename(st_fips = state) %>%
  rename(cnty_fips = county) %>%
  select(-c("qje72b", "qje72c", "pop70", "oldcode"))

# Include HS expenditures in county for kid at age 4 in census dataset
# cfips90 column of census1980 is FIPS code of <state, county> combo
census1980 <- inner_join(census1980, hsspend_df, by = c("cnty_fips", "st_fips"))
census1980$hsspend_at_four <- rep(0, nrow(census1980))
idx <- which(census1980$birthyr==1964)
census1980$hsspend_at_four[idx] <- census1980$hsspend68[idx]
idx <- which(census1980$birthyr==1965)
census1980$hsspend_at_four[idx] <- census1980$hsspend69[idx]
idx <- which(census1980$birthyr==1966)
census1980$hsspend_at_four[idx] <- census1980$hsspend70[idx]
idx <- which(census1980$birthyr==1967)
census1980$hsspend_at_four[idx] <- census1980$hsspend71[idx]
idx <- which(census1980$birthyr==1968)
census1980$hsspend_at_four[idx] <- census1980$hsspend72[idx]
```

Adding demographic characteristics

```{r}
# other non hispanic and black non hispanic
census1980$othernh <- as.integer(census1980$race != 1 & census1980$race != 0 & census1980$hispan == 0)
census1980$blacknh <- as.integer(census1980$race == 2 & census1980$hispan == 0)
census1980$whitenh <- as.integer(census1980$race == 1 & census1980$hispan == 0)
census1980$hispanic <- as.integer(census1980$hispan > 0)
census1980$female <- as.integer(census1980$sex == 2)
```

Grade-for-age status
- In general the ages and grades really don't match up. The first people were born 21 years before 1980 but the highest grade observed is fifth.
    - e.g. the first few people are second graders who'd be 13 years old...
    - These seem much more like 1970 numbers! In 1970, only a few kids born between 1959 and 1968 would be old enough to be fifth graders, as we observe. 
(Jimmy) I'm not sure I see what you mean, if you do a call to `unique(census1980$gradeatt)` there are codes from 0 to 7, and looking at the coding for `gradeatt` on the census website, 1 is preschool, 7 is graduate/professional school.

The variable they use is `higraded`, detailed info about the highest grade attended for each individual.
First, we try to compute what grade they are in (including if they failed to finish, are currently attending, or have finished, I think; the extra details around this are a bit confusing but I'll replicate what the paper did.)

```{r}
gradelevel <- rep(NA, nrow(census1980))
# not started grade school yet
gradelevel[census1980$higraded <= '030'] <- 0
# at least started first grade
gradelevel[census1980$higraded >= '031' & census1980$higraded <= '040'] <- 1
# at least started second grade
gradelevel[census1980$higraded >= '041' & census1980$higraded <= '050'] <- 2
# at least started third grade
gradelevel[census1980$higraded >= '051' & census1980$higraded <= '060'] <- 3
# at least started fourth grade
gradelevel[census1980$higraded >= '061' & census1980$higraded <= '070'] <- 4
# at least started fifth grade
gradelevel[census1980$higraded >= '071' & census1980$higraded <= '080'] <- 5
# at least started sixth grade
gradelevel[census1980$higraded >= '081' & census1980$higraded <= '090'] <- 6
# at least started seventh grade
gradelevel[census1980$higraded >= '091' & census1980$higraded <= '100'] <- 7
# at least started eighth grade
gradelevel[census1980$higraded >= '101' & census1980$higraded <= '110'] <- 8
# at least started ninth grade
gradelevel[census1980$higraded >= '111' & census1980$higraded <= '120'] <- 9
# at least started tenth grade
gradelevel[census1980$higraded >= '121' & census1980$higraded <= '130'] <- 10
# at least started eleventh grade
gradelevel[census1980$higraded >= '131' & census1980$higraded <= '140'] <- 11
# at least started twelfth grade, but did not finish
gradelevel[census1980$higraded >= '141' & census1980$higraded <= '142'] <- 12
# high school graduate, or better
gradelevel[census1980$higraded >= '150'] <- 13

census1980 <- census1980 %>% mutate(gradelevel = gradelevel) 
```

Now, let's try to compute the grade we expect each individual to at least be in, assuming they are
on track with their state's schooling requirements.

```{r}
convstate <- read_dta(paste0(raw_path, 'convstate.dta'))
convstate$st_fips <- sprintf("%02s", convstate$stfips)
census1980 <- inner_join(x=census1980, y=convstate, by = 'st_fips')

cutoff_qtr <- rep(NA, nrow(census1980))
# cutoffs from Cascio et al
q1s <- census1980$stname %in% c('AL', 'CT', 'DE', 'FL', 'MS', 'NM', 'VT', 'PA')
q3s <- census1980$stname %in% c('CO', 'DE', 'KS', 'MD', 'MN', 'MT', 'TX', 'UT',
                                'NH', 'IA', 'WY', 'MO', 'TN', 'VA', 'GA', 'IN', 'MA', 'WA')
cutoff_qtr[q1s] <- 1
cutoff_qtr[q3s] <- 3
cutoff_qtr[is.na(cutoff_qtr)] <- 4
census1980$cutoff_qtr <- cutoff_qtr

# now, get the years in which they can start first grade (using cutoffs from Cascio et al)
# can start first grade in the school year starting with 6 years after the year of birth
# if they were born in quarters 1 and 2
# assume, like the paper, that q3 births miss the q3 cutoff for states, and must start 7 yrs after
# also, assume that q4 births miss both q3 and q4 cutoffs for relevant states, so must start 7 yrs after

schoolstart <- census1980$birthyr+6
census1980$schoolstart <- schoolstart
exception1 <- census1980$birthqtr == 3 & census1980$cutoff_qtr == 3
exception2 <- census1980$birthqtr == 4 & census1980$cutoff_qtr >= 3
schoolstart[exception1] = census1980$birthyr[exception1] + 7
schoolstart[exception2] = census1980$birthyr[exception2] + 7
expected_grade <- 1980 - schoolstart
expected_grade[expected_grade >= 13] = 13
census1980$expected_grade = expected_grade
census1980$at_gradelvl <- as.integer(census1980$gradelevel >= census1980$expected_grade)
```

Now, let's add an indicator about whether an individual was a preschooler when SS
started airing in 1969 (meaning, if an individual started first grade after 1969,
they would have been in preschool when SS came out).

```{r}
# Column for whether preschool age, per paper
census1980$preschool1969 <- as.integer(census1980$schoolstart > 1969)
```

Now, let's try to replicate Figure 5:

```{r}
avg_cov <- mean(census1980$pred_cov)
low_cov <- census1980 %>% filter(pred_cov <= avg_cov) %>% group_by(schoolstart) %>% summarize(prop_gradelvl = mean(at_gradelvl))
high_cov <- census1980 %>% filter(pred_cov > avg_cov) %>% group_by(schoolstart) %>% summarize(prop_gradelvl = mean(at_gradelvl))
cov_comparison <- low_cov %>% rename(low = prop_gradelvl) %>% mutate(high = high_cov$prop_gradelvl)

ggplot(cov_comparison) + geom_col(aes(x = as.factor(schoolstart), y = high-low)) + xlab('Expected Year of Beginning School') + ylab('Difference in Proportions between \n High and Low Areas') + ggtitle('Comparing Proportions of At-Grade Level Children with High vs. Low Coverage') + theme_light()

```
Seems pretty good! Agrees with what their plot shows (For cohorts already starting school before Sesame Street was airing, differences in grade level status between high and low coverage areas is less pronounced then after Sesame Street began).

Now, let's try to fit the regression:

```{r}
# I think they do a logistic regression? The STATA command doesn't seem to explicitly
# do this, but we have a binary response, so let's just do something

# concatenate state and county fips into single code
census1980$full_cty_fips <- paste0(census1980$st_fips, census1980$cnty_fips)

# Pretty sure they define birth cohorts by when they were supposed to start school 
reg_dat <- census1980 %>% select(hsspend_at_four, fs_available, female, momhsdrop,
                                 momhsgrad, blacknh, othernh, hispanic, 
                                 full_cty_fips, stname, schoolstart, 
                                 preschool1969, pred_cov, at_gradelvl, whitenh)
reg_dat <- reg_dat %>% mutate(preschool_cov = preschool1969*pred_cov)
```

# Models to Fit

## Model 1: As Close to Their Model 1 No Fixed Effects

Mainly trying to Replicate first two rows of Table 4

```{r}
mean(reg_dat$at_gradelvl)
```

```{r}
# takes really long to fit all of the fixed effects (county level + state x birth cohort)
# starting with just not fitting the fixed effects
logistic_mod1 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool1969:pred_cov, 
                     family = 'binomial', data = reg_dat)

summary(logistic_mod1)
```

```{r}
mean(reg_dat %>% filter(female == 0) %>% select(at_gradelvl) %>% unlist())
```

```{r}
logistic_mod1 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool1969:pred_cov, 
                     family = 'binomial', data = reg_dat %>% filter(female == 0))

summary(logistic_mod1)
```


```{r}
mean(reg_dat %>% filter(female == 1) %>% select(at_gradelvl) %>% unlist())
```

```{r}
logistic_mod1 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool1969:pred_cov, 
                     family = 'binomial', data = reg_dat %>% filter(female == 1))

summary(logistic_mod1)
```

```{r}
mean(reg_dat %>% filter(whitenh == 1) %>% select(at_gradelvl) %>% unlist())
```

```{r}
logistic_mod1 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + momhsdrop + female +
                       momhsgrad + preschool1969:pred_cov, 
                     family = 'binomial', data = reg_dat %>% filter(whitenh == 1))

summary(logistic_mod1)
```

```{r}
mean(reg_dat %>% filter(blacknh == 1) %>% select(at_gradelvl) %>% unlist())
```

```{r}
logistic_mod1 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + pred_cov:preschool1969, 
                     family = 'binomial', data = reg_dat %>% filter(blacknh == 1))

summary(logistic_mod1)
```

```{r}
mean(reg_dat %>% filter(hispanic == 1) %>% select(at_gradelvl) %>% unlist())
```

```{r}
logistic_mod1 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + pred_cov:preschool1969, 
                     family = 'binomial', data = reg_dat %>% filter(hispanic == 1))

summary(logistic_mod1)
```

```{r}
logistic_mod1 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + pred_cov:preschool1969, 
                     family = 'binomial', data = reg_dat %>% filter(hispanic == 1))

summary(logistic_mod1)
```

I'm fitting the models a little bit different than they did; I think they include the demographic terms
even though they're subsetting by demographic variable which is kinda weird. 

## Model 2: As Close to Their Model 2, No Fixed Effects

Repeating the third rows basically.

```{r}
reg_dat <- reg_dat %>% mutate(preschool6768 = as.integer(reg_dat$schoolstart >= 1967 & reg_dat$schoolstart <= 1968)) %>%
  mutate(preschool69 = as.integer(reg_dat$schoolstart == 1969)) %>%
  mutate(preschool7072 = as.integer(reg_dat$schoolstart >= 1970 & reg_dat$schoolstart <= 1972)) %>%
  mutate(preschool7374 = as.integer(reg_dat$schoolstart >= 1973 & reg_dat$schoolstart <= 1974))

logistic_mod2 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool6768:pred_cov + 
                       preschool69:pred_cov + preschool7072:pred_cov + preschool7374:pred_cov, 
                     family = 'binomial', data = reg_dat)

summary(logistic_mod2)
```
Corroborates one of their findings: that different cohorts have different impacts of SS coverage
on their outcomes, and that it's specifically the later ones, or the ones that would have
had more exposure to SS in their pre-k, for which the effect of coverage is particularly high.
However, maybe we should take the actual magnitudes themselves with a grain of salt, since
fitting their full models is virtually impossible.

```{r}
logistic_mod2 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool6768:pred_cov + 
                       preschool69:pred_cov + preschool7072:pred_cov + preschool7374:pred_cov, 
                     family = 'binomial', data = reg_dat %>% filter(female == 0))

summary(logistic_mod2)
```

```{r}
logistic_mod2 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool6768:pred_cov + 
                       preschool69:pred_cov + preschool7072:pred_cov + preschool7374:pred_cov, 
                     family = 'binomial', data = reg_dat %>% filter(female == 1))

summary(logistic_mod2)
```
Less of an effect for girls vs. boys, especially as you get into later cohorts! Other note: I think the transition from negative to positive is partly due to in 1965 there being more at-grade level students in higher coverage areas than in lower coverage areas,
at least with how we cleaned the data.

```{r}
logistic_mod2 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + preschool6768:pred_cov + 
                       preschool69:pred_cov + preschool7072:pred_cov + preschool7374:pred_cov, 
                     family = 'binomial', data = reg_dat %>% filter(whitenh == 1))

summary(logistic_mod2)
```

```{r}
logistic_mod2 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + preschool6768:pred_cov + 
                       preschool69:pred_cov + preschool7072:pred_cov + preschool7374:pred_cov, 
                     family = 'binomial', data = reg_dat %>% filter(blacknh == 1))

summary(logistic_mod2)
```
Biggest effects for black students, especially in later cohorts. This is basically what they observed!

```{r}
logistic_mod2 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + preschool6768:pred_cov + 
                       preschool69:pred_cov + preschool7072:pred_cov + preschool7374:pred_cov, 
                     family = 'binomial', data = reg_dat %>% filter(hispanic == 1))

summary(logistic_mod2)
```
Much smaller effect for hispanic students relative to other demographic groups, which is also what the paper observed.

## Model 3: Repeating the First Model, but Redefining the Treatment Variable as Above Average Coverage

```{r}
# define at least 60% coverage as being in a high-coverage area
reg_dat <- reg_dat %>% mutate(high_cov = as.integer(reg_dat$pred_cov > 60))

# takes really long to fit all of the fixed effects (county level + state x birth cohort)
# starting with just not fitting the fixed effects
logistic_mod3 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + high_cov:preschool1969, 
                     family = 'binomial', data = reg_dat)

summary(logistic_mod3)
```
## Model 4: Repeating the Second Model, but Redefining the Treatment Variable as Above Average Coverage

```{r}
logistic_mod4 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + preschool6768*high_cov + 
                       preschool69*high_cov + preschool7072*high_cov + preschool7374*high_cov, 
                     family = 'binomial', data = reg_dat)

summary(logistic_mod4)
```
Looking at this is pretty interesting. Being in an area of high coverage seems to increase your odds of
being at grade level, and then being in later cohorts increases the effect even higher (so there is treatment effect heterogeneity here).

## Model 5: Take Four Large US States that are Broadly Representative of the Country, and make that the 'US' and fit the fixed effects models

## Outcome Regression Model 1:

```{r}
logistic_mod6 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + 
                       preschool1969:pred_cov + factor(full_cty_fips) + factor(stname):factor(schoolstart), 
                     family = 'binomial', data = reg_dat %>% filter(stname %in% c('FL', 'NY', 'CA', 'TX')))

logistic_mod6$coefficients['preschool1969:pred_cov']
```

## Outcome Regression Model 2:

```{r}
logistic_mod7 <- glm(at_gradelvl ~ hsspend_at_four + fs_available + female + momhsdrop +
                       momhsgrad + blacknh + othernh + hispanic + 
                       preschool6768:pred_cov + preschool69:pred_cov + preschool7072:pred_cov + 
                       preschool7374:pred_cov + factor(full_cty_fips) + factor(stname):factor(schoolstart), 
                     family = 'binomial', data = reg_dat %>% filter(stname %in% c('FL', 'NY', 'CA', 'TX')))

logistic_mod7$coefficients['preschool6768:pred_cov']
logistic_mod7$coefficients['pred_cov:preschool69']
logistic_mod7$coefficients['pred_cov:preschool7072']
logistic_mod7$coefficients['pred_cov:preschool7374']
```

Looks good as well, we're increasing in likelihood. At least for this regression, our results
are more comparable to the table since we are also still fitting the fixed effects. However,
there are important differences that qualify any such comparison (like we're using a different model, for ex.)
